Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic: adapted to CHOP input format

### 2021-12-16 psy_peds_3_CHOP.Rmd
select the correct column to do the lm, time_p instead of time

```{r, its count based}
ts_linear_count <- lm(count_psy_patients ~ period * time, patient_count_psy_period_psy)
ts_linear_count_clear <- lm(count_psy_patients ~ period * time, patient_count_psy_period_psy_clear)
ts_seasonal_count <- lm(count_psy_patients ~ period*time + harmonic(month_year, 1, 12), patient_count_psy_period_psy)
ts_seasonal_count_clear <- lm(count_psy_patients ~ period*time + harmonic(month_year, 1, 12), patient_count_psy_period_psy_clear)
```

```{r, its percentage based}
ts_linear_percent <- lm(percentage ~ period * time, patient_count_psy_period_psy)
ts_linear_percent_clear <- lm(percentage ~ period * time, patient_count_psy_period_psy_clear)
ts_seasonal_percent <- lm(percentage ~ period*time + harmonic(month_year, 1, 12), patient_count_psy_period_psy)
ts_seasonal_percent_clear <- lm(percentage ~ period*time + harmonic(month_year, 1, 12), patient_count_psy_period_psy_clear)
```

@@

bootstrapped_sample_list <- vector(mode = "list", length = bootstrap_size)
bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
for (iteration in 1:bootstrap_size) {
  df_iteration <- data.frame(period = patient_count_psy_period_psy$period,
                             time = patient_count_psy_period_psy$time,
                             percentage = bootstrapped_timepoints[iteration, ])
  ts_linear_percent <- lm(percentage ~ period * time, df_iteration)
  linear_model <- broom::tidy(ts_linear_percent) %>%
    filter(term %in% c("time", "periodduring_pandemic:time"))
  coefficients <- linear_model$estimate
  names(coefficients) <- linear_model$term
  bootstrapped_coefficients_list[[iteration]] <- coefficients
  df_iteration$predicted <- predict(ts_linear_percent)
  df_iteration$time_p <- patient_count_psy_period_psy$time_p
  bootstrapped_sample_list[[iteration]] <- df_iteration
}

>>>>

```{r, its count based}
ts_linear_count <- lm(count_psy_patients ~ period * time_p, patient_count_psy_period_psy)
ts_linear_count_clear <- lm(count_psy_patients ~ period * time_p, patient_count_psy_period_psy_clear)
ts_seasonal_count <- lm(count_psy_patients ~ period*time_p + harmonic(month_year, 1, 12), patient_count_psy_period_psy)
ts_seasonal_count_clear <- lm(count_psy_patients ~ period*time_p + harmonic(month_year, 1, 12), patient_count_psy_period_psy_clear)
```

```{r, its percentage based}
ts_linear_percent <- lm(percentage ~ period * time_p, patient_count_psy_period_psy)
ts_linear_percent_clear <- lm(percentage ~ period * time_p, patient_count_psy_period_psy_clear)
ts_seasonal_percent <- lm(percentage ~ period*time_p + harmonic(month_year, 1, 12), patient_count_psy_period_psy)
ts_seasonal_percent_clear <- lm(percentage ~ period*time_p + harmonic(month_year, 1, 12), patient_count_psy_period_psy_clear)
```

@@

bootstrapped_sample_list <- vector(mode = "list", length = bootstrap_size)
bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
for (iteration in 1:bootstrap_size) {
  df_iteration <- data.frame(period = patient_count_psy_period_psy$period,
                             time = patient_count_psy_period_psy$time_p,
                             percentage = bootstrapped_timepoints[iteration, ])
  ts_linear_percent <- lm(percentage ~ period * time, df_iteration)
  linear_model <- broom::tidy(ts_linear_percent) %>%
    filter(term %in% c("time", "periodduring_pandemic:time"))
  coefficients <- linear_model$estimate
  names(coefficients) <- linear_model$term
  bootstrapped_coefficients_list[[iteration]] <- coefficients
  df_iteration$predicted <- predict(ts_linear_percent)
  df_iteration$time_p <- patient_count_psy_period_psy$time_p
  bootstrapped_sample_list[[iteration]] <- df_iteration
}
